Recurrent Neural Networks

### 2017-09-05 deeplearn/presentation/presentation_slides.tex
moved presentation

\begin{frame}{Recurrent Neural Networks}
  \begin{itemize}
  \item Recurrent neural networks are just a prescription for a class of functions of the form $f:\R^n\times \R^\ell\times\R^m\to \R^\ell\times \R^m$, where $\R^m$ is the space of parameters.
  \item The set $\{0, 1\}^*$ of all finite sequences of $0$'s and $1$'s is countable,
  \item and $\R^\ell$, is a real vector space,
  is uncountable.
  \item Therefore, we can encode every element $w\in\{0, 1\}^*$ as a vector in $S$.  Informally,
  $\R^\ell$ is enough to encode any finite state space, and every possible value for the content of the tape of a Turing machine. We get:
  {\em Recurrent neural networks are Turing-complete.}
  \item This explains why recurrent neural networks seem to be able to produce results that other networks can't.
  \item Training a recurrent network is the same as producing a Turing machine.
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Recurrent Neural Networks}
  \begin{itemize}
  \item Recurrent neural networks are just a prescription for a class of functions of the form $$f:\R^n\times \R^\ell\times\R^m\to \R^\ell\times \R^m$$ where $\R^m$ is the space of parameters.\pause
  \item The set $\{0, 1\}^*$ of all finite sequences of $0$'s and $1$'s is countable,
  \item and $\R^\ell$, is uncountable.
  \item We can encode every element $w\in\{0, 1\}^*$ as a vector in $S$.  Informally,
  $\R^\ell$ is enough to encode any finite state space, and every possible value for the content of the tape of a Turing machine. We get:
  {\em Recurrent neural networks are Turing-complete.}
  \item This explains why recurrent neural networks seem to be able to produce results that other networks can't.
  \item Training a recurrent network is the same as producing a Turing machine.
\end{itemize}
\end{frame}
